Meta-analysis

### 2020-06-23 04_MetaAnalysis.Rmd
delete random bits of code
Typos, code corrections, and plotting order

The sample variance is a similar formula except we use $x$ instead of $y$.
$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
Therefore: 
$S_{Var} = \frac{1}{n_{x}} \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1} $  
Where $n_x$ is the number of samples within each treatment.

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

dat1$trial[1]

@@

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5, 1.5, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()

max(slimmer_PM_dat[slimmer_PM_dat$cluster_1 == "Late" &
                      ,"fungicide_timing_1"], na.rm = TRUE)
```

@@

We also want to know if disease pressure exerts an effect on the desicion for spray control.
Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
Does this change between years of low and high disease pressure.

>>>>

The sample variance is a similar formula except we use $x$ instead of $y$.
$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
Therefore: 
$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
Where $n_x$ is the number of samples within each treatment.

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management - 1,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 24.4769, df = 5, p = 0.0002$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.76, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

@@

```{r metafor_plot}
efficacy %>%
   mutate(Treatment = factor(Treatment, levels = rev(c("Early", "Recommended", "Recommended_plus","Late","Late_plus"))))%>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.4, 1.8, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0)+
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()

@@

We also want to know if disease pressure exerts an effect on the desicion for spray control.
Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
Does this change between years of low and high disease pressure.
